---
title: 'Assignment: 9.2 Exercise'
author: "Raghuwanshi, Prashant"
date: '2021-08-06'
output: pdf_document
---

# Question no 1 : Complete assignment09

### Fit a Logistic Regression Model to Thoracic Surgery Binary Dataset
### For this problem, you will be working with the thoracic surgery data set from the University of California Irvine machine learning repository. 
### This dataset contains information on life expectancy in lung cancer patients after surgery. The underlying thoracic surgery data is in ARFF format. 
### This is a text-based format with information on each of the attributes. You can load this data using a package such as foreign or by cutting and pasting the data section into a CSV file.
```{r}
library(ggplot2)
theme_set(theme_minimal())
library(readxl)
### Set the working directory to the root of your DSC 520 directory

setwd("D:/MS_DataScience/DSC 520-Datastatiics.pdf/dsc520")

### Load the `data/ThoraricSurgery.csv` to
th_surgery_df <- read.csv("data/ThoraricSurgery.csv")
str(th_surgery_df)
### Assignment Instructions:
```
### Fit a binary logistic regression model to the data set that predicts whether or not the patient survived for one year (the Risk1Y variable) after the surgery.
### Use the glm() function to perform the logistic regression. See Generalized Linear Models for an example. Include a summary using the summary() function in your results.
```{r}
logistic_model <- glm(Risk1Yr ~ ., family = binomial(), th_surgery_df)
summary(logistic_model)
### According to the summary, which variables had the greatest effect on the survival rate?
### ANS seems PRE14 variable is having greatest effect on survival rate
```
### To compute the accuracy of your model, use the dataset to predict the outcome variable. 
### The percent of correct predictions is the accuracy of your model. What is the accuracy of your model?
### Subsetting the data and keeping the required variables
```{r}
surgery_df1 <- th_surgery_df[ ,c("Risk1Yr", "PRE14", "PRE17")]
### Checking the dim
dim(surgery_df1)
### Converting to factor variables
surgery_df1$Risk1Yr <- as.factor(surgery_df1$Risk1Yr)
surgery_df1$PRE14 <- as.factor(surgery_df1$PRE14)
surgery_df1$PRE17 <- as.factor(surgery_df1$PRE17)
### Loading caret library
require(caret)
### Splitting the data into train and test
index <- createDataPartition(surgery_df1$Risk1Yr, p = .70, list = FALSE)
train <- surgery_df1[index, ]
test <- surgery_df1[-index, ]
### Training the model
logistic_model1 <- glm(Risk1Yr ~ ., family = binomial(), train)
### Checking the model
summary(logistic_model1)
### Converting from probability to actual output
train$pred_Risk1Yr <- ifelse(logistic_model1$fitted.values >= 0.5, "False", "True")
### Generating the classification table
ctab_train <- table(train$Risk1Yr, train$pred_Risk1Yr)
### Predicting in the test dataset
pred_prob <- predict(logistic_model1, test, type = "response")
### Generating the classification table
ctab_train <- table(train$Risk1Yr, train$pred_Risk1Yr)
### Converting from probability to actual output
test$pred_Risk1Yr <- ifelse(pred_prob >= 0.5, "False", "True")
# Generating the classification table
ctab_test <- table(test$Risk1Yr, test$pred_Risk1Yr)
ctab_test
```
### Accuracy = (TP + TN)/(TN + FP + FN + TP)
# Accuracy in Training dataset
```{r}
accuracy_train <- sum(diag(ctab_train))/sum(ctab_train)*100
accuracy_train
# Accuracy in Test dataset
accuracy_test <- sum(diag(ctab_test))/sum(ctab_test)*100
accuracy_test
```
# 2 Fit a Logistic Regression Model
### Fit a logistic regression model to the binary-classifier-data.csv dataset
```{r}
library(ggplot2)
theme_set(theme_minimal())
library(readxl)
### Set the working directory to the root of your DSC 520 directory

setwd("D:/MS_DataScience/DSC 520-Datastatiics.pdf/dsc520")

### Load the `data/ThoraricSurgery.csv` to
binary_df <- read.csv("data/binary-classifier-data.csv")
str(binary_df)
require(caret)
### Splitting the data into train and test
index_bin <- createDataPartition(binary_df$label, p = .70, list = FALSE)
train_bin <- binary_df[index, ]
test_bin <- binary_df[-index, ]
### Training the model
logistic_model_bin <- glm(label ~ x + y, family = binomial(), train_bin)
### Checking the model
summary(logistic_model_bin)
### Converting from probability to actual output
train_bin$pred_label <- ifelse(logistic_model_bin$fitted.values >= 0.5, 0, 1)
### Generating the classification table
ctab_train_bin <- table(train_bin$label, train_bin$pred_label)
### Predicting in the test dataset
pred_prob_bin <- predict(logistic_model_bin, test_bin, type = "response")
### Converting from probability to actual output
### Accuracy = (TP + TN)/(TN + FP + FN + TP)
### Accuracy in Training dataset
accuracy_train_bin <- sum(diag(ctab_train_bin))/sum(ctab_train_bin)*100
accuracy_train_bin
### Keep this assignment handy, as you will be comparing your results from this week to next week
```