---
title: "Assignment: 9.2 Final Project Step 2"
author: "Raghuwanshi, Prashant"
date: '2021-08-07'
Note: Included Step 1 Details along with Step 2
output: pdf_document
---

# Introduction

### Credit score cards are a common risk control method in the financial industry. 
### It uses personal information and data submitted by credit card applicants to predict the probability of future defaults and credit card borrowings. 
### The bank is able to decide whether to issue a credit card to the applicant. Credit scores can objectively quantify the magnitude of risk.
### I want to perform below EDA on the top of credit card application data
### split out the data and try to found the correlation , dependent variables, independent variables
### outliers and biased for the given data set. this will help me researches on the best variables which the credit
### card company give more importance while issuing new card to  the best fited card member

# Research questions

### Q find out outliers in all variables and removed outlier records from dataframe
### find out the correlation between numeric variables and plot the correlation using various technique
### fit liner regression model and find the most significant variables in df
### do credit default and applicant annual income have strong significance
### do applicant with long employment and age can be consider to qualify for credit card

# Approach

### How your approach addresses (fully or partially) the problem.
###my approach will focus on below lsited three points
###1 Getting a better understanding of data
###2 Identifying various data patterns
###3 Getting a better understanding of the problem statement
### below steps which requried to address above points
### Checking Introductory Details About Data
### Statistical Insight
### Data cleaning
### Checking Duplicates
### Data Visualization
### Multi-Variate analysisVarious Plots
### Here EDA approach will give the right inofrmation for dependent and multiple independent varibales
### which is going to help me in identifying the closes fit independent variable
### which help researcher to recommend the card types to  the cities and gender types 

# Data  (2 Datasets - but no requirement on number of fields or rows)

### https://www.kaggle.com/rikdifos/credit-card-approval-prediction?select=credit_record.csv
### https://www.kaggle.com/rikdifos/credit-card-approval-prediction?select=application_record.csv

# Required Packages
```{r}
library(ggplot2)
theme_set(theme_minimal())
library(readxl)
library(tidyverse)
library(dplyr)
library(QuantPsyc)
library(gridExtra)
library(car)
library(PerformanceAnalytics)
library("GGally")
```
# Plots and Table Needs

###Correlation Matrix
###Scatterplot
###pairplot
###Histogram
###Boxplot

# Questions for future steps

### find out the correlation among variables
### club application and credit report for current month
### perform EDA by using R programming


# How to import and clean my data
```{r}
### Set the working directory to the root of your DSC 520 directory
setwd("D:/MS_DataScience/DSC 520-Datastatiics.pdf/dsc520")
### Load card data `data/credit_record.csv` to DF
credit_df <- read.csv("data/credit_record.csv")
### Cleaning records, by filtering out old records and keep current credit record
credit_val <- filter(credit_df, MONTHS_BALANCE==0)
head(credit_val)

### Load credit card application data `data/application_record.csv` to DF
appl_df <- read.csv("data/application_record.csv")

### Join the credit data with application data and find out current credit status
card_df <- merge(x = appl_df, y = credit_val, by = "ID", all.x = TRUE)
head(card_df)
### fixing missing value,defaulting the missed month balance & status as 0
card_df$MONTHS_BALANCE <- factor(ifelse( is.na(card_df$MONTHS_BALANCE), 0, card_df$MONTHS_BALANCE))
card_df$STATUS <- factor(ifelse( is.na(card_df$STATUS), 0, card_df$STATUS))
### factoring variables
card_df$CODE_GENDER <- factor(card_df$CODE_GENDER)
card_df$FLAG_OWN_CAR <- factor(card_df$FLAG_OWN_CAR)
card_df$FLAG_OWN_REALTY <- factor(card_df$FLAG_OWN_REALTY)
card_df$NAME_EDUCATION_TYPE <- factor(card_df$NAME_EDUCATION_TYPE)
```
# What does the final data set look like?

### Preparing new data set with required City, Date, Card.Type, Exp.Type, Gender, Amount, Tier fields
```{r}
head(card_df)
str(card_df)
dim(card_df)
summary(card_df)
```
# How do you plan to slice and dice the data?
```{r}
card_df1 <- dplyr::select(card_df, ID, CNT_CHILDREN, AMT_INCOME_TOTAL, DAYS_BIRTH, DAYS_EMPLOYED, STATUS)
card_df2 <- filter(card_df1, STATUS==1)
card_df3 <- dplyr::select(card_df2, CNT_CHILDREN, AMT_INCOME_TOTAL, DAYS_BIRTH, DAYS_EMPLOYED)
dim(card_df3)
```
# Questions for future steps

### Q find out outliers in all variables and removed outlier records from dataframe
### find out the correlation between numeric variables and plot the correlation using various technique
### fit liner regression model and find the most significant variables in df
### do credit default and applicant annual income have strong significance
### do applicant with long employment and age can be consider to qualify for credit card

# What types of plots and tables will help you to illustrate the findings to your questions?
```{r}
### Correlation Matrix
chart.Correlation(card_df3, histogram=TRUE, pch=19)
### In the above plot:
### The distribution of each variable is shown on the diagonal.
### On the bottom of the diagonal : the bivariate scatter plots with a fitted line are displayed
### On the top of the diagonal : the value of the correlation plus the significance level as stars
### Each significance level is associated to a symbol : p-values(0, 0.001, 0.01, 0.05, 0.1, 1) <=> symbols(???***???, ???**???, ???*???, ???.???, " ???)
```

### correlation
```{r}
res <- cor(card_df3)
round(res, 2)
```
### corrplot
```
library(corrplot)
corrplot(res, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)

### Positive correlations are displayed in blue and negative correlations in red color. 
### Color intensity and the size of the circle are proportional to the correlation coefficients. 
### In the right side of the correlogram, the legend color shows the correlation coefficients and the corresponding colors.
```
### boxplot to find out outlier and removed outlier value from my dataset
```{r}
boxplot(card_df3)
boxplot(card_df3$AMT_INCOME_TOTAL)
### Now you can assign the outlier values into a vector
outliers_AMT_INCOME_TOTAL <- boxplot(card_df3$AMT_INCOME_TOTAL, plot=FALSE)$out
### Check the results
print(outliers_AMT_INCOME_TOTAL)
### First you need find in which rows the outliers are
card_df3[which(card_df3$AMT_INCOME_TOTAL %in% outliers_AMT_INCOME_TOTAL),]
card_df4 <- card_df3[-which(card_df3$AMT_INCOME_TOTAL %in% outliers_AMT_INCOME_TOTAL),]
### If you check now with boxplot, you will notice that those pesky outliers are gone
boxplot(card_df4)
```
### Scatter plots with multiple groups
```{r}
# Change point shapes by the levels of STATUS
ggplot(card_df1, aes(x=DAYS_BIRTH, y=AMT_INCOME_TOTAL, shape=STATUS)) +
  geom_point() + geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
# Change point shapes by the levels of STATUS
ggplot(card_df, aes(x=DAYS_BIRTH, y=AMT_INCOME_TOTAL, shape=CODE_GENDER)) +
  geom_point() + geom_smooth(method=lm, se=FALSE, fullrange=TRUE)
```
### Pairplot
```{r}
pairs(card_df2)
ggpairs(card_df2)
ggpairs(card_df4)
```
# How could you summarize your data to answer key questions?
```{r}
linearMod <- lm(AMT_INCOME_TOTAL ~ STATUS + CNT_CHILDREN +DAYS_BIRTH + DAYS_EMPLOYED, data=card_df1) 
summary(linearMod)

plot(fitted(linearMod), resid(linearMod))

qqnorm(resid(linearMod))
```
# What information is not self-evident
```{r}
logMod <- glm(STATUS ~ AMT_INCOME_TOTAL + CNT_CHILDREN +DAYS_BIRTH + DAYS_EMPLOYED, data=card_df, family=binomial(link='logit')) 
summary(logMod)
logMod2 <- glm(CODE_GENDER ~ AMT_INCOME_TOTAL + CNT_CHILDREN +DAYS_BIRTH + DAYS_EMPLOYED, data=card_df, family=binomial(link='logit')) 
summary(logMod2)
logMod3 <- glm(FLAG_OWN_REALTY ~ AMT_INCOME_TOTAL + CNT_CHILDREN +DAYS_BIRTH + DAYS_EMPLOYED, data=card_df, family=binomial(link='logit')) 
summary(logMod3)
logMod4 <- glm(FLAG_OWN_REALTY ~ STATUS + CNT_CHILDREN +DAYS_BIRTH + DAYS_EMPLOYED, data=card_df, family=binomial(link='logit')) 
summary(logMod4)
```
# Do you plan on incorporating any machine learning techniques to answer your research questions? Explain
### will do in final step

# Questions for future steps
### which ml techniques is suitable for my model
### want to add some more questions based on plotted results
